---
title: "Inclusivity of Shades in the Make Up Industry"
output:
  html_document:
    df_print: paged
---

#Installing Packages 
```{r}
#install.packages("tidyverse")
#install.packages("psych")
```

#Load library
```{r}
library(tidyverse)
library(psych)
```

#Read file
```{r}
shades <- read_csv("shades.csv")
shades
```

#Notes 
##Lightness indicates wether a foundation line is for lighter or darker skintones. 

##High saturation means that the colors appear to be more pure. 

##Brightness and value - intensity of the light or perceived luminance. 

##Hue would be like the undertone. It is either more yellow and warm, more pink, more olive... 

```{r}
summary(shades)
```

#deleting the products for wich i do not have some values 
```{r}
shades_1 <- drop_na(shades)
shades_1
```
```{r}
summary(shades_1)
```



#Changing <chr> to factor 
```{r}
shades_1$brand <- factor(shades_1$brand)
shades_1$brand_short <- factor(shades_1$brand_short)
shades_1$product <- factor(shades_1$product)
shades_1$product_short <- factor(shades_1$product_short)
shades_1$hex <- factor(shades_1$hex)
```

```{r}
head(shades_1)
```

#Creatign subsets by brand
```{r}
shades_addiction <- subset(shades_1, brand == "Addiction") 
shades_addiction
shades_bareMinerals <- subset(shades_1, brand == "bareMinerals") 
shades_bareMinerals
shades_bareMinerals <- subset(shades_1, brand == "bareMinerals") 
shades_bareMinerals
shades_Beauty_Bakerie <- subset(shades_1, brand == "Beauty Bakerie") 
shades_Beauty_Bakerie
shades_Bharat_Doris <- subset(shades_1, brand == "Bharat & Doris") 
shades_Bharat_Doris
shades_Black_Opal <- subset(shades_1, brand == "Black Opal") 
shades_Black_Opal
shades_Black_Up <- subset(shades_1, brand == "Black Up")
shades_Black_Up
shades_Bobbi_Brown <- subset(shades_1, brand == "Bobbi Brown")
shades_Bobbi_Brown
shades_Colorbar <- subset(shades_1, brand == "Colorbar")
shades_Colorbar
shades_Estée_Lauder <- subset(shades_1, brand == "Estée Lauder")
shades_Estée_Lauder
shades_Fenty <- subset(shades_1, brand == "Fenty")
shades_Fenty
shades_Hegai_and_Ester <- subset(shades_1, brand == "Hegai and Ester")
shades_Hegai_and_Ester
shades_House_of_Tara <- subset(shades_1, brand == "House of Tara")
shades_House_of_Tara
shades_Iman <- subset(shades_1, brand == "Iman")
shades_Iman
shades_IPSA <- subset(shades_1, brand == "IPSA")
shades_IPSA
shades_LOreal <- subset(shades_1, brand == "L'Oréal")
shades_LOreal
shades_Lancome <- subset(shades_1, brand == "Lancôme")
shades_Lancome
shades_Laws_of_Nature <- subset(shades_1, brand == "Laws of Nature")
shades_Laws_of_Nature
shades_MAC <- subset(shades_1, brand == "MAC")
shades_MAC
shades_Maybelline <- subset(shades_1, brand == "Maybelline")
shades_Maybelline
shades_Make_Up_For_Ever <- subset(shades_1, brand == "Make Up For Ever")
shades_Make_Up_For_Ever
shades_NARS <- subset(shades_1, brand == "NARS")
shades_NARS
shades_Revlon <- subset(shades_1, brand == "Revlon")
shades_Revlon
shades_Shu_Uemera <- subset(shades_1, brand == "Shu Uemera")
shades_Shu_Uemera
shades_Trim_Prissy <- subset(shades_1, brand == "Trim & Prissy")
shades_Trim_Prissy
shades_Shiseido <- subset(shades_1, brand == "Shiseido")
shades_Shiseido
```
#For Fenty - Blacked owned
##Pairs pannel to see any correlation. There is a very high correlation between lightness and brightness. Moreover, these same two are the ones that define the color names. There fore, if we are looking at fenty's make up, we would know that the biggest change from shade to shade comes from the brightness and the lightness. 
```{r}
pairs.panels(shades_Fenty)
```

#Looking at the count of how spread their lightness is on their products. 
```{r}
p <- ggplot(data = shades_Fenty, 
            mapping = aes(x = L)) + 
            geom_histogram() +
            labs(title = "Fenty Lightness",
                 x = "Percentage of Lightness",
                 y = "Count")
p

#Thre is a fair spread of their lightness use in different shades. Having a slightly bigger use of lighter since there is a bigger demand for it. 
```


```{r}
ggplot(data = shades_Fenty) +
  geom_density(mapping = aes(x = L, fill = product , alpha = 01)) +
  labs(title = "Histogram: Fenty Lightness by Product",
       x = "Lightness",
       y = "Count")       
```



#For Mayballine - Not Black Owned 
```{r}
pairs.panels(shades_Maybelline)
```

```{r}
p <- ggplot(data = shades_Maybelline, 
            mapping = aes(x = L)) + 
            geom_histogram() +
            labs(title = "Maybelline Lightness",
                 x = "Percentage of Lightness",
                 y = "Count")
p

#Maybelline does provide all shades of lightness, but they have a higher focus on lighter colors compared to Fenty beauty which was more even. 
```


```{r}
ggplot(data = shades_Maybelline) +
  geom_density(mapping = aes(x = L, fill = product , alpha = 01)) +
  labs(title = "Histogram: Maybelline Lightness by Product",
       x = "Lightness",
       y = "Count")    
```

```{r}
#First the two product lines are going ot be separated 

fit_me <- filter(shades_Maybelline, product == "Fit Me")
fit_me_matte <- filter(shades_Maybelline, product == "Fit Me Matte")

shapiro.test(fit_me$L)
shapiro.test(fit_me_matte$L)
```


#Since the p-value is greater than 0.05, then we would consider it normal.
##For T-Test: 
## If p-value is >= alpha(0.05) NOT significantly different 
## If p-value is <= alpha(0.05)  significantly different 
```{r}
t.test(fit_me$L, fit_me_matte$L, paired = FALSE)
#Since the p-value (3.819e-06) is smaller than 0.05. The two shades use of lightness is are significantly different. 
```





#Beauty Bakerie - Blacked owned 
##Surprisingly out the brands selected, this one is the only one for which the hue had any relevance to the color shade. 
```{r}
pairs.panels(shades_Beauty_Bakerie)
```

```{r}
p <- ggplot(data = shades_Beauty_Bakerie, 
            mapping = aes(x = L)) + 
            geom_histogram() +
            labs(title = "Beauty Bakerie Lightness",
                 x = "Percentage of Lightness",
                 y = "Count")
p
```
```{r}
ggplot(data = shades_Beauty_Bakerie) +
  geom_density(mapping = aes(x = L, fill = product , alpha = 01)) +
  labs(title = "Histogram: Beauty Bakerie Lightness by Product",
       x = "Lightness",
       y = "Count")    
```


#Estee Lauder 
```{r}
pairs.panels(shades_Estée_Lauder)
```

```{r}
p <- ggplot(data = shades_Estée_Lauder, 
            mapping = aes(x = L)) + 
            geom_histogram() +
            labs(title = "Estee Lauder Lightness",
                 x = "Percentage of Lightness",
                 y = "Count")
p
```

```{r}
ggplot(data = shades_Estée_Lauder) +
  geom_density(mapping = aes(x = L, fill = product , alpha = 01)) +
  labs(title = "Histogram: Estee Lauder Lightness by Product",
       x = "Lightness",
       y = "Count")    
```


#L'Oreal
```{r}
pairs.panels(shades_LOreal)
```

```{r}
p <- ggplot(data = shades_LOreal, 
            mapping = aes(x = L)) + 
            geom_histogram() +
            labs(title = "L'Oreal Lightness",
                 x = "Percentage of Lightness",
                 y = "Count")
p
```


```{r}
ggplot(data = shades_LOreal) +
  geom_density(mapping = aes(x = L, fill = product , alpha = 01)) +
  labs(title = "Histogram: Fenty Lightness by Product",
       x = "Lightness",
       y = "Count")    
```

#Normality: Shapiro for Loreal Two products lines as of the lightness. 
```{r}
#Filter groups 1 and 2 
infalliable <- filter(shades_LOreal, product == "Infalliable")
true_match <- filter(shades_LOreal,  product == "True Match")

#Test each group's extra for normality 
shapiro.test(infalliable$L)
shapiro.test(true_match$L)

#Since the p value is smaller than 0.05 it is considered not normal 

## If P-values are less than 0.05. The distribution is significantly different from a Known normal distriburion. Not a normal distribution.  
```

#Mann_Whitney-Wilcoxon Test: since the shapiro test came as Non-Normally Distributed 
## wilcox.test(<vector1>, <vector2>, paired = TRUE/FALSE)

```{r}
#wilcox.test(infalliable$L, true_match$L, paired = FALSE)\
##Since the result is > 0.05 then we would assume there is weaker evidance of a null hypthesis. there is not enough difference between the shades of infallible and true match. 
```

#Trime & Prissy: Black owned 
```{r}
pairs.panels(shades_Trim_Prissy)
```


```{r}
t <- ggplot(data = shades_Trim_Prissy, 
       mapping = aes(x = L)) +
       geom_histogram() +
       labs(title = "Trim & Prissy Lightness",
                 x = "Percentage of Lightness",
                 y = "Count")
t
```


```{r}
ggplot(data = shades_Trim_Prissy) +
  geom_density(mapping = aes(x = L, fill = product , alpha = 01)) +
  labs(title = "Histogram: Trim & Prissy Lightness by Product",
       x = "Lightness",
       y = "Count")    
```



```{r}
flawless_finish <- filter(shades_Trim_Prissy, product == "Flawless Finish")
hi_def <- filter(shades_Trim_Prissy, product == "Hi - Def" )
```


```{r}
shapiro.test(flawless_finish$L)
shapiro.test(hi_def$L)

#Both p-values are higher than 0.05 Both distributions are not significantly different from a know normally distribution. Therefore we assume NORMALITY
```

```{r}
t.test(flawless_finish$L, hi_def$L, paired = FALSE)
#The p-value is again > 0.05 which means they are not significantly different. 
```



#Thank you! 
##Carmen Lazaro 



